Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-06-30 documents/cpm.tex
tiny abstract changes

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science ---
the most precise photometric measurements of stars ever made ---
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level; So that
it can capture more fine-grained information about the variation of the spacecraft.
The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star. In addition, we use the target star’s future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components), which we set by cross-validation. 
We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
We find that we can consistently outperform (for the purposes of exoplanet detection) 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.

>>>>

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science---% no spaces around ---
the most precise photometric measurements of stars ever made---%
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level so that
it can capture very fine-grained information about the variation of the spacecraft.
The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star. In addition, we use the target star’s future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components), which we set by cross-validation. 
We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
We find that we can consistently outperform (for the purposes of exoplanet detection) 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.
